---
title: "Journal (reproducible report)"
author: "Julian Glaßmeyer"
date: "2020-11-25"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```


# My first post

Last compiled: `r Sys.Date()`

# Data Science at TUHH ------------------------------------------------------
# SALES ANALYSIS ----

# 1.0 Load libraries ----

```{r}
library(tidyverse)
library(readxl)
library(lubridate)
library(writexl)
library(rvest)     # HTML Hacking & Web Scraping
library(xopen)     # Quickly opening URLs
library(jsonlite)  # converts JSON files to R objects
library(glue)      # concatenate strings
library(stringi)   # character string/text processing
library(httr)
library(glue)
library(jsonlite)
```

# 2.0 Importing Files ----
```{r}
bikes_tbl      <- read_excel(path = "00_data/01_bike_sales/01_raw_data/bikes.xlsx")
orderlines_tbl <- read_excel("00_data/01_bike_sales/01_raw_data/orderlines.xlsx")
bikeshops_tbl  <- read_excel("00_data/01_bike_sales/01_raw_data/bikeshops.xlsx")
```

# 4.0 Joining Data ----
```{r}
bike_orderlines_joined_tbl <- orderlines_tbl %>%
  left_join(bikes_tbl, by = c("product.id" = "bike.id")) %>%
  left_join(bikeshops_tbl, by = c("customer.id" = "bikeshop.id"))
```


# 5.0 Wrangling Data ----
```{r}
bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
  separate(col    = category,
           into   = c("category.1", "category.2", "category.3"),
           sep    = " - ") %>%
  mutate(total.price = price * quantity) %>%
  select(-...1, -gender) %>%
  select(-ends_with(".id")) %>%
  bind_cols(bike_orderlines_joined_tbl %>% select(order.id)) %>% 
  select(order.id, contains("order"), contains("model"), contains("category"),
         price, quantity, total.price,
         everything()) %>%
  rename(bikeshop = name) %>%
  set_names(names(.) %>% str_replace_all("\\.", "_"))
```


# 6.0 Business Insights ----
# 6.1 Sales by Year ----

# Step 1 - Manipulate
```{r}
sales_by_year_tbl <- bike_orderlines_wrangled_tbl %>%
  select(order_date, total_price) %>%
  mutate(year = year(order_date)) %>%
  group_by(year) %>% 
  summarize(sales = sum(total_price)) %>%
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))
```


# Step 2 - Visualize
```{r}
sales_by_year_tbl %>%
  ggplot(aes(x = year, y = sales)) +
  geom_col(fill = "#2DC6D6") + 
  geom_label(aes(label = sales_text)) + 
  geom_smooth(method = "lm", se = FALSE) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title    = "Revenue by year",
    subtitle = "Upward Trend",
    x = "",
    y = "Revenue"
  )
```


# 6.2 Sales by Year and Category 2 ----

# Step 1 - Manipulate
```{r}
sales_by_year_cat_1_tbl <- bike_orderlines_wrangled_tbl %>%
  select(order_date, total_price, category_1) %>%
  mutate(year = year(order_date)) %>%
  group_by(year, category_1) %>%
  summarise(sales = sum(total_price)) %>%
  ungroup() %>%
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))
```


# Step 2 - Visualize
```{r}
sales_by_year_cat_1_tbl %>%
  ggplot(aes(x = year, y = sales, fill = category_1)) +
  geom_col() +
  facet_wrap(~ category_1) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue by year and main category",
    subtitle = "Each product category has an upward trend",
    fill = "Main category"
  )
```


# 7.0 Writing Files ----

# 7.1 Excel ----
```{r}
bike_orderlines_wrangled_tbl %>%
  write_xlsx("00_data/01_bike_sales/02_wrangled_data/bike_orderlines.xlsx")
```

# 7.2 CSV ----
```{r}
bike_orderlines_wrangled_tbl %>% 
  write_csv("00_data/01_bike_sales/02_wrangled_data/bike_orderlines.csv")
```

# 7.3 RDS ----
```{r}
bike_orderlines_wrangled_tbl %>% 
  write_rds("00_data/01_bike_sales/02_wrangled_data/bike_orderlines.rds")
```

# 8 Challenge ----
# Step 1 - Manipulate
```{r}
bike_state_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
  separate(col    = category,
           into   = c("category.1", "category.2", "category.3"),
           sep    = " - ") %>%
  separate(col    = location,
           into   = c("city", "state"),
           sep    = ", ") %>%
  mutate(total.price = price * quantity) %>%
  select(-...1, -gender) %>%
  select(-ends_with(".id")) %>%
  bind_cols(bike_orderlines_joined_tbl %>% select(order.id)) %>% 
  select(order.id, contains("order"), contains("model"), contains("category"),
         price, quantity, total.price,
         everything()) %>%
  rename(bikeshop = name) %>%
  set_names(names(.) %>% str_replace_all("\\.", "_"))
```

```{r}
sales_by_state_tbl <- bike_state_orderlines_wrangled_tbl %>%
  select(state, total_price) %>%
  group_by(state) %>% 
  summarize(sales = sum(total_price)) %>%
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))
```

```{r}
sales_by_state_tbl
```

# Step 2 - Visualize
```{r}
sales_by_state_tbl %>%
  ggplot(aes(x = state, y = sales)) +
  geom_col(fill = "#2DC6D6") + 
  geom_label(aes(label = sales_text)) + 
  geom_smooth(method = "lm", se = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title    = "Revenue by State",
    subtitle = "",
    x = "State",
    y = "Revenue"
  )
```

# Analyze the sales by location and year ----
# Step 1 - Manipulate
```{r}
sales_by_year_state_tbl <- bike_state_orderlines_wrangled_tbl %>%
  select(order_date, total_price, state) %>%
  mutate(year = year(order_date)) %>%
  group_by(year, state) %>%
  summarise(sales = sum(total_price)) %>%
  ungroup() %>%
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))
```

# Step 2 - Visualize

# Baden-Württemberg
```{r}
sales_by_year_state_tbl %>%
  ggplot(aes(x = "Baden-Württemberg", y = sales, fill = year)) +
  geom_col() +
  facet_wrap(~ year) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue in Baden-Württemberg by year",
    subtitle = "",
    fill = "Main category"
  )
```


# Bavaria
```{r}
sales_by_year_state_tbl %>%
  ggplot(aes(x = "Bavaria", y = sales, fill = year)) +
  geom_col() +
  facet_wrap(~ year) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue in Bavaria by year",
    subtitle = "",
    fill = "Main category"
  )
```

# Berlin
```{r}
sales_by_year_state_tbl %>%
  ggplot(aes(x = "Berlin", y = sales, fill = year)) +
  geom_col() +
  facet_wrap(~ year) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue in Berlin by year",
    subtitle = "",
    fill = "Main category"
  )
```

# Bremen
```{r}
sales_by_year_state_tbl %>%
  ggplot(aes(x = "Bremen", y = sales, fill = year)) +
  geom_col() +
  facet_wrap(~ year) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue in Bremen by year",
    subtitle = "",
    fill = "Main category"
  )
```

# Hamburg
```{r}
sales_by_year_state_tbl %>%
  ggplot(aes(x = "Hamburg", y = sales, fill = year)) +
  geom_col() +
  facet_wrap(~ year) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue in Hamburg by year",
    subtitle = "",
    fill = "Main category"
  )

```

# Hesse 
```{r}
sales_by_year_state_tbl %>%
  ggplot(aes(x = "Hesse", y = sales, fill = year)) +
  geom_col() +
  facet_wrap(~ year) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue in Hesse by year",
    subtitle = "",
    fill = "Main category"
  )
```


# Lower Saxony
```{r}
sales_by_year_state_tbl %>%
  ggplot(aes(x = "Lower Saxony", y = sales, fill = year)) +
  geom_col() +
  facet_wrap(~ year) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue in Lower Saxony by year",
    subtitle = "",
    fill = "Main category"
  )
```


# Mecklenburg-Western Pomerania 
```{r}
sales_by_year_state_tbl %>%
  ggplot(aes(x = "Mecklenburg-Western Pomerania", y = sales, fill = year)) +
  geom_col() +
  facet_wrap(~ year) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue in Mecklenburg-Western Pomerania by year",
    subtitle = "",
    fill = "Main category"
  )
```


# North Rhine-Westphalia 
```{r}
sales_by_year_state_tbl %>%
  ggplot(aes(x = "North Rhine-Westphalia", y = sales, fill = year)) +
  geom_col() +
  facet_wrap(~ year) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue in North Rhine-Westphalia by year",
    subtitle = "",
    fill = "Main category"
  )
```


# Saxony 
```{r}
sales_by_year_state_tbl %>%
  ggplot(aes(x = "Saxony", y = sales, fill = year)) +
  geom_col() +
  facet_wrap(~ year) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue in Saxony by year",
    subtitle = "",
    fill = "Main category"
  )
```


# Saxony-Anhalt
```{r}
sales_by_year_state_tbl %>%
  ggplot(aes(x = "Saxony-Anhalt", y = sales, fill = year)) +
  geom_col() +
  facet_wrap(~ year) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue in Saxony-Anhalt by year",
    subtitle = "",
    fill = "Main category"
  )
```


# Schleswig-Holstein
```{r}
sales_by_year_state_tbl %>%
  ggplot(aes(x = "Schleswig-Holstein", y = sales, fill = year)) +
  geom_col() +
  facet_wrap(~ year) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue in Schleswig-Holstein by year",
    subtitle = "",
    fill = "Main category"
  )
```


# Weather Data for Hamburg
```{r}
hamburg_weather <- GET("http://api.openweathermap.org/data/2.5/weather?q=Hamburg,DE&APPID=fc851c17b49d940f2315af23e7efb62d")
hamburg_weather
rawToChar(hamburg_weather$content)
hamburg_weather %>% 
  .$content %>% 
  rawToChar() %>% 
  fromJSON()
```


# Road bikes from Rose with prices

```{r}
url_rennrad          <- "https://www.rosebikes.de/fahrräder/rennrad"
html_rennrad         <- read_html(url_rennrad)
rennrad_tbl <- html_rennrad %>%
  html_nodes(css = ".catalog-category-bikes__title") %>%
  html_text() %>%
  enframe(name = "position", value = "family_class") %>%
  mutate(
    family_class = str_glue("#{family_class}")
  )
rennrad_prices_tbl <- html_rennrad %>%
  html_nodes(css = ".catalog-category-bikes__price-title") %>%
  html_text() %>%
  enframe(name = "position", value = "price") %>%
  mutate(
    price = str_glue("#{price}")
  )

bind_cols(rennrad_tbl, rennrad_prices_tbl)
```

