---
title: "Journal (reproducible report)"
author: "Julian Glaßmeyer"
date: "2020-11-25"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

Last compiled: `r Sys.Date()`

# Business Data Science Basics TUHH

## Load libraries
```{r}
library(tidyverse)
library(readxl)
library(lubridate)
library(writexl)
library(rvest)     # HTML Hacking & Web Scraping
library(xopen)     # Quickly opening URLs
library(jsonlite)  # converts JSON files to R objects
library(glue)      # concatenate strings
library(stringi)   # character string/text processing
library(httr)
library(glue)
library(jsonlite)
library(vroom)
library(tictoc)
```

```{r}
bikes_tbl      <- read_excel(path = "00_data/01_bike_sales/01_raw_data/bikes.xlsx")
orderlines_tbl <- read_excel("00_data/01_bike_sales/01_raw_data/orderlines.xlsx")
bikeshops_tbl  <- read_excel("00_data/01_bike_sales/01_raw_data/bikeshops.xlsx")
```

```{r}
bike_orderlines_joined_tbl <- orderlines_tbl %>%
  left_join(bikes_tbl, by = c("product.id" = "bike.id")) %>%
  left_join(bikeshops_tbl, by = c("customer.id" = "bikeshop.id"))
```

```{r}
bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
  separate(col    = category,
           into   = c("category.1", "category.2", "category.3"),
           sep    = " - ") %>%
  mutate(total.price = price * quantity) %>%
  select(-...1, -gender) %>%
  select(-ends_with(".id")) %>%
  bind_cols(bike_orderlines_joined_tbl %>% select(order.id)) %>% 
  select(order.id, contains("order"), contains("model"), contains("category"),
         price, quantity, total.price,
         everything()) %>%
  rename(bikeshop = name) %>%
  set_names(names(.) %>% str_replace_all("\\.", "_"))
```

```{r}
sales_by_year_tbl <- bike_orderlines_wrangled_tbl %>%
  select(order_date, total_price) %>%
  mutate(year = year(order_date)) %>%
  group_by(year) %>% 
  summarize(sales = sum(total_price)) %>%
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))
```

```{r}
sales_by_year_tbl %>%
  ggplot(aes(x = year, y = sales)) +
  geom_col(fill = "#2DC6D6") + 
  geom_label(aes(label = sales_text)) + 
  geom_smooth(method = "lm", se = FALSE) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title    = "Revenue by year",
    subtitle = "Upward Trend",
    x = "",
    y = "Revenue"
  )
```

```{r}
sales_by_year_cat_1_tbl <- bike_orderlines_wrangled_tbl %>%
  select(order_date, total_price, category_1) %>%
  mutate(year = year(order_date)) %>%
  group_by(year, category_1) %>%
  summarise(sales = sum(total_price)) %>%
  ungroup() %>%
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))
```

```{r}
sales_by_year_cat_1_tbl %>%
  ggplot(aes(x = year, y = sales, fill = category_1)) +
  geom_col() +
  facet_wrap(~ category_1) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue by year and main category",
    subtitle = "Each product category has an upward trend",
    fill = "Main category"
  )
```

```{r}
bike_orderlines_wrangled_tbl %>%
  write_xlsx("00_data/01_bike_sales/02_wrangled_data/bike_orderlines.xlsx")
```

```{r}
bike_orderlines_wrangled_tbl %>% 
  write_csv("00_data/01_bike_sales/02_wrangled_data/bike_orderlines.csv")
```

```{r}
bike_orderlines_wrangled_tbl %>% 
  write_rds("00_data/01_bike_sales/02_wrangled_data/bike_orderlines.rds")
```

# Intro to the tidyverse
## Challenge 1

```{r}
bike_state_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
  separate(col    = category,
           into   = c("category.1", "category.2", "category.3"),
           sep    = " - ") %>%
  separate(col    = location,
           into   = c("city", "state"),
           sep    = ", ") %>%
  mutate(total.price = price * quantity) %>%
  select(-...1, -gender) %>%
  select(-ends_with(".id")) %>%
  bind_cols(bike_orderlines_joined_tbl %>% select(order.id)) %>% 
  select(order.id, contains("order"), contains("model"), contains("category"),
         price, quantity, total.price,
         everything()) %>%
  rename(bikeshop = name) %>%
  set_names(names(.) %>% str_replace_all("\\.", "_"))
```

```{r}
sales_by_state_tbl <- bike_state_orderlines_wrangled_tbl %>%
  select(state, total_price) %>%
  group_by(state) %>% 
  summarize(sales = sum(total_price)) %>%
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))
```

```{r}
sales_by_state_tbl
```

### Visualization
```{r}
sales_by_state_tbl %>%
  ggplot(aes(x = state, y = sales)) +
  geom_col(fill = "#2DC6D6") + 
  geom_label(aes(label = sales_text)) + 
  geom_smooth(method = "lm", se = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title    = "Revenue by State",
    subtitle = "",
    x = "State",
    y = "Revenue"
  )
```

## Challenge 2

```{r}
sales_by_year_state_tbl <- bike_state_orderlines_wrangled_tbl %>%
  select(order_date, total_price, state) %>%
  mutate(year = year(order_date)) %>%
  group_by(year, state) %>%
  summarise(sales = sum(total_price)) %>%
  ungroup() %>%
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))
```

###Visualization

### Baden-Württemberg
```{r}
sales_by_year_state_tbl %>%
  ggplot(aes(x = "Baden-Württemberg", y = sales, fill = year)) +
  geom_col() +
  facet_wrap(~ year) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue in Baden-Württemberg by year",
    subtitle = "",
    fill = "Main category"
  )
```


### Bavaria
```{r}
sales_by_year_state_tbl %>%
  ggplot(aes(x = "Bavaria", y = sales, fill = year)) +
  geom_col() +
  facet_wrap(~ year) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue in Bavaria by year",
    subtitle = "",
    fill = "Main category"
  )
```

### Berlin
```{r}
sales_by_year_state_tbl %>%
  ggplot(aes(x = "Berlin", y = sales, fill = year)) +
  geom_col() +
  facet_wrap(~ year) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue in Berlin by year",
    subtitle = "",
    fill = "Main category"
  )
```

### Bremen
```{r}
sales_by_year_state_tbl %>%
  ggplot(aes(x = "Bremen", y = sales, fill = year)) +
  geom_col() +
  facet_wrap(~ year) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue in Bremen by year",
    subtitle = "",
    fill = "Main category"
  )
```

### Hamburg
```{r}
sales_by_year_state_tbl %>%
  ggplot(aes(x = "Hamburg", y = sales, fill = year)) +
  geom_col() +
  facet_wrap(~ year) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue in Hamburg by year",
    subtitle = "",
    fill = "Main category"
  )

```

### Hesse 
```{r}
sales_by_year_state_tbl %>%
  ggplot(aes(x = "Hesse", y = sales, fill = year)) +
  geom_col() +
  facet_wrap(~ year) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue in Hesse by year",
    subtitle = "",
    fill = "Main category"
  )
```


### Lower Saxony
```{r}
sales_by_year_state_tbl %>%
  ggplot(aes(x = "Lower Saxony", y = sales, fill = year)) +
  geom_col() +
  facet_wrap(~ year) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue in Lower Saxony by year",
    subtitle = "",
    fill = "Main category"
  )
```


### Mecklenburg-Western Pomerania 
```{r}
sales_by_year_state_tbl %>%
  ggplot(aes(x = "Mecklenburg-Western Pomerania", y = sales, fill = year)) +
  geom_col() +
  facet_wrap(~ year) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue in Mecklenburg-Western Pomerania by year",
    subtitle = "",
    fill = "Main category"
  )
```


### North Rhine-Westphalia 
```{r}
sales_by_year_state_tbl %>%
  ggplot(aes(x = "North Rhine-Westphalia", y = sales, fill = year)) +
  geom_col() +
  facet_wrap(~ year) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue in North Rhine-Westphalia by year",
    subtitle = "",
    fill = "Main category"
  )
```


### Saxony 
```{r}
sales_by_year_state_tbl %>%
  ggplot(aes(x = "Saxony", y = sales, fill = year)) +
  geom_col() +
  facet_wrap(~ year) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue in Saxony by year",
    subtitle = "",
    fill = "Main category"
  )
```

### Saxony-Anhalt
```{r}
sales_by_year_state_tbl %>%
  ggplot(aes(x = "Saxony-Anhalt", y = sales, fill = year)) +
  geom_col() +
  facet_wrap(~ year) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue in Saxony-Anhalt by year",
    subtitle = "",
    fill = "Main category"
  )
```

### Schleswig-Holstein
```{r}
sales_by_year_state_tbl %>%
  ggplot(aes(x = "Schleswig-Holstein", y = sales, fill = year)) +
  geom_col() +
  facet_wrap(~ year) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue in Schleswig-Holstein by year",
    subtitle = "",
    fill = "Main category"
  )
```


# Data Acquisition
## Weather Data for Hamburg

```{r}
hamburg_weather <- GET("http://api.openweathermap.org/data/2.5/weather?q=Hamburg,DE&APPID=fc851c17b49d940f2315af23e7efb62d")
hamburg_weather
rawToChar(hamburg_weather$content)
hamburg_weather %>% 
  .$content %>% 
  rawToChar() %>% 
  fromJSON()
```


## Scraping Rose website - Road bikes with prices
```{r}
url_rennrad          <- "https://www.rosebikes.de/fahrräder/rennrad"
html_rennrad         <- read_html(url_rennrad)
rennrad_tbl <- html_rennrad %>%
  html_nodes(css = ".catalog-category-bikes__title") %>%
  html_text() %>%
  enframe(name = "position", value = "family_class") %>%
  mutate(
    family_class = str_glue("#{family_class}")
  )
rennrad_prices_tbl <- html_rennrad %>%
  html_nodes(css = ".catalog-category-bikes__price-title") %>%
  html_text() %>%
  enframe(name = "position", value = "price") %>%
  mutate(
    price = str_glue("#{price}")
  )

bind_cols(rennrad_tbl, rennrad_prices_tbl)
```

# Data Wrangling
```{r}
col_types <- list(
  id = col_character(),
  type = col_character(),
  number = col_character(),
  country = col_character(),
  date = col_date("%Y-%m-%d"),
  abstract = col_character(),
  title = col_character(),
  kind = col_character(),
  num_claims = col_double(),
  filename = col_character(),
  withdrawn = col_double()
)

patent_tbl <- vroom(
  file       = "patent.tsv", 
  delim      = "\t", 
  col_types  = col_types,
  na         = c("", "NA", "NULL")
)

class(patent_tbl)
setDT(patent_tbl)
class(patent_tbl)

col_types <- list(
  id = col_character(),
  type = col_character(),
  number = col_character(),
  country = col_character(),
  date = col_date("%Y-%m-%d"),
  abstract = col_character(),
  title = col_character(),
  kind = col_character(),
  num_claims = col_double(),
  filename = col_character(),
  withdrawn = col_double()
)

assignee_tbl <- vroom(
  file       = "assignee.tsv", 
  delim      = "\t", 
  col_types  = col_types,
  na         = c("", "NA", "NULL")
)

class(assignee_tbl)
setDT(assignee_tbl)
class(assignee_tbl)

col_types <- list(
  id = col_character(),
  type = col_character(),
  number = col_character(),
  country = col_character(),
  date = col_date("%Y-%m-%d"),
  abstract = col_character(),
  title = col_character(),
  kind = col_character(),
  num_claims = col_double(),
  filename = col_character(),
  withdrawn = col_double()
)
patent_assignee_tbl <- vroom(
  file       = "patent_assignee.tsv", 
  delim      = "\t", 
  col_types  = col_types,
  na         = c("", "NA", "NULL")
)

class(patent_assignee_tbl)
setDT(patent_assignee_tbl)
class(patent_assignee_tbl)

col_types <- list(
  id = col_character(),
  type = col_character(),
  number = col_character(),
  country = col_character(),
  date = col_date("%Y-%m-%d"),
  abstract = col_character(),
  title = col_character(),
  kind = col_character(),
  num_claims = col_double(),
  filename = col_character(),
  withdrawn = col_double()
)

uspc_tbl <- vroom(
  file       = "uspc.tsv", 
  delim      = "\t", 
  col_types  = col_types,
  na         = c("", "NA", "NULL")
)
```

## Question 1
### Patent Dominance: What US company / corporation has the most patents? List the 10 US companies with the most assigned/granted patents in 2014.

```{r}
setnames(assignee_tbl, "id", "assignee_id")

combined_data <- merge(x = patent_assignee_tbl, y = assignee_tbl, 
                       by    = "assignee_id", 
                       all.x = TRUE, 
                       all.y = FALSE)

combined_data_us <- combined_data %>%
  filter(type == "2")

combined_data_us %>%
  group_by(organization) %>%
  summarise(
    count = n(),
  ) %>%
  ungroup() %>%
  arrange(desc(count)) %>% 
  head(10)

```


## Question 2
### What US company had the most patents granted in April 2014?

```{r}
setnames(patent_tbl, "id", "patent_id")

combined_data_us_date <- merge(x = combined_data_us, y = patent_tbl, 
                       by    = "patent_id", 
                       all.x = TRUE, 
                       all.y = FALSE)

combined_data_us_date$date <- as.Date(combined_data_us_date$date, format= "%Y-%m-%d")

combined_data_us_april <- subset(combined_data_us_date, date> "2014-04-01" & date < "2014-04-30")

combined_data_us_april %>%
  group_by(organization) %>%
  summarise(
    count = n(),
  ) %>%
  ungroup() %>%
  arrange(desc(count)) %>% 
  head(10)

```

## Question 3
```{r}
combined_data_3 <- merge(x = patent_assignee_tbl, y = assignee_tbl, 
                               by    = "assignee_id", 
                               all.x = TRUE, 
                               all.y = FALSE)

combined_data_3_uspc <- merge(x = uspc_tbl, y = combined_data_3, 
                         by    = "patent_id", 
                         all.x = TRUE, 
                         all.y = FALSE)

```

### Top 5 USPTO main classes 
```{r}
combined_data_3_uspc %>%
  group_by(mainclass_id) %>%
  summarise(
    count = n(),
  ) %>%
  ungroup() %>%
  arrange(desc(count)) %>% 
  head(5)
```

### Top 10 companies worldwide with most patents
```{r}
combined_data_3 %>%
  group_by(organization) %>%
  summarise(
    count = n(),
  ) %>%
  ungroup() %>%
  arrange(desc(count)) %>% 
  head(10)
```

# Data visualization
```{r}
covid_data_tbl <- read_csv("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv")
```

## Challenge 1
```{r}
covid_data_tbl %>% 
   distinct(cases, dateRep, countriesAndTerritories) %>% 
   filter(countriesAndTerritories == 'Germany' | 
            countriesAndTerritories == 'United_Kingdom' | 
            countriesAndTerritories == 'Spain' | 
            countriesAndTerritories == 'France' | 
            countriesAndTerritories == 'United_States_of_America') %>%
   mutate(date       = lubridate::dmy(dateRep)) %>%
   arrange(date) %>% 
   group_by(countriesAndTerritories) %>% 
   mutate(cumsum = cumsum(cases)) %>% 
   ggplot() +
   geom_line(aes(x     = date,
                 y     = cumsum,
                 color = countriesAndTerritories))
```

## Challenge 2

```{r}
world <- map_data("world")
```

```{r}
covid_data_tbl %>% 
  distinct(cases, dateRep, countriesAndTerritories, popData2019) %>% 
  filter(countriesAndTerritories == 'Germany' | 
           countriesAndTerritories == 'United_Kingdom' | 
           countriesAndTerritories == 'Spain' | 
           countriesAndTerritories == 'France' | 
           countriesAndTerritories == 'United_States_of_America')
```

```{r}
covid_data_tbl_rates <- covid_data_tbl %>%
  mutate(across(countriesAndTerritories, str_replace_all, "_", " ")) %>%
  mutate(countriesAndTerritories = case_when(
    countriesAndTerritories == "United Kingdom" ~ "UK",
    countriesAndTerritories == "United States of America" ~ "USA",
    countriesAndTerritories == "Czechia" ~ "Czech Republic",
    TRUE ~ countriesAndTerritories
  )) %>%
  group_by(countriesAndTerritories) %>% 
  summarise(total_deaths = sum(deaths), pop = mean(popData2019)) %>% 
  ungroup() %>%
  rename(region = countriesAndTerritories)
```

```{r}
combined_data_1 <- merge(x = world, y = covid_data_tbl_rates, 
                         by    = "region",
                         all.x = TRUE, 
                         all.y = FALSE)
```

```{r}
plot_data_1 <- combined_data_1 %>% 
  distinct(pop, region, long, lat, total_deaths) %>%
  group_by(region) %>%
  mutate(pct = (total_deaths / pop)*100) %>%
  ungroup()
```

### Visualization of the distribution of the mortality rate worldwide

```{r}
plot_data_1 %>%  ggplot() +
  geom_map (aes(map_id = region, fill = pct), map = world, color = "white") + 
  expand_limits(x = world$long,  y = world$lat) +
  scale_fill_viridis_c(option = "D")
```







